Promotors' reports on the first draft of the thesis document.

### 2020-09-09 ChapterRampInput/ChapterRampInput.tex
One before the very last

\begin{quote}
\vspace{-0.5cm}
\emph{The results of this chapter were published in Quintana Carapia, G., and Markovsky, I.,
"Input parameters estimation from time-varying measurements", Measurement Journal, Vol. 153, 2020,
ISSN 0263-2241, doi:10.1016/j.measurement.2019.107418. \nocite{QuintanaMEAS} }\vfill{}
\end{quote}

%\vfill{}

@@

\paragraph{Problem} 
Given the sequence of measured output observations $\widetilde{\mathbf{y}} = \left( \widetilde{y}(1),\ldots, \widetilde{y}(\color{blue}N\color{black})\right)$, with $\widetilde{y}(t) \in \mathbb{R}$, of a stable linear time-invariant system of order $n$, and static gain ${G}$, generated by an affine input $u(t) = {a} t + {b}$, estimate the parameters of the affine input, \textit{i.e.,} find the values of the parameters $\widehat{a}, \widehat{b} \in {\rm I\!R}$ such that $\widehat{u}(t) = \widehat{a} t + \widehat{b}$ approximates $u$(t).
The measured observations $\widetilde{\mathbf{y}} = {\mathbf{y}} + \bm{\epsilon}$ are exact sensor responses ${\mathbf{y}}$ perturbed by additive noise  $\bm{\epsilon}$ assumed to be independent and normally distributed of zero mean and given variance $\sigma_{\epsilon}^2$.

@@

The subspace method processed online the sensor transient response.
The first estimation was obtained with $2n+1$ samples, where $n=2$ is the assumed order of the sensor.
The method updated recursively the value of the estimated parameters for each new collected sample, using the forgetting factor $\omega$ listed in Table \ref{table:lambdas}.
In Figure \ref{fig:rele_dd_40dB_s1} we observe the relative errors of the estimates $\widehat{a}$ and $\widehat{b}$ obtained when SNR = 40 dB. 
The relative errors are smaller than 5 \% after 400 and 500 samples are processed, i.e., 0.04 s and 0.05 s, respectively.
As more samples are collected, the parameter estimation improves.
Figure \ref{fig:rele_SNR_dd_10000} shows the final value of the relative errors, found at $t=0.1$ s, for the different SNR values considered.
The relative errors are smaller than 2 \% regardless of the measurement noise level.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_3.pdf} 
\caption{ \label{fig:rele_dd_40dB_s1} The relative errors of the affine input parameters estimates decrease as the subspace method processes more samples. The relative errors of the estimates $\widehat{a}$ and $\widehat{b}$ are smaller than 5 \% after 400 and 500 samples, respectively ($T_s = 0.1$ ms). }
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_4.pdf} 
\caption{ \label{fig:rele_SNR_dd_10000} The minimum value of the estimation relative errors obtained with the subspace method is less than 2  \% regardless of the SNR between 20 dB and 60 dB. }
\end{figure}

@@

\subsection{Results of the maximum-likelihood method}
\color{blue} 
The maximum-likelihood (ML) method estimates the affine input parameters from the sensor model transient response.
A total of 100 runs of the method were obtained, using different realizations of the measurement noise.
The measurement noise variance was set to have an SNR of 40 dB.
The ML method used the first 50 samples to initialize the optimization variables and updated the variables every $N_{\mathrm{s}} = 5$ samples.
Figure \ref{fig:rele_lo_40dB_s10} shows the average of the observed relative errors in the estimation of the parameters $\widehat{a}$, $\widehat{b}$, $\widehat{x}_{\mathrm{ini,1}}$, and $\widehat{x}_{\mathrm{ini,2}}$\color{black}.
The convergence of the ML estimates gives relative errors below 5 \% after three iterations.
The largest relative error observed is in the scale velocity $\widehat{x}_{\mathrm{ini,2}}$ estimate, which is more sensitive than the other optimization variables.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_7.pdf} 
\caption{ \label{fig:rele_lo_40dB_s10} The affine input parameters and the sensor's initial conditions are estimated with the ML method. After three iterations, \color{blue} the average of the relative error is smaller than 5 \% for each and every of the estimates. The estimate $\widehat{x}_{\mathrm{ini,2}}$ has the larger relative error near to 1 \%. \color{black} }
\end{figure}

@@

Figure \ref{fig:rele_tv_40dB_s1} shows the relative errors of the estimates $\widehat{a}$ and $\widehat{b}$ computed with the TV filter after processing the sensor transient response.
The relative error of the slope estimate is below 5 \% after 300 samples but the relative error of the intercept estimate is near 10 \%.
The convergence rate of the estimate $\widehat{a}$ was similar to that of the subspace method.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_9.pdf} 
\caption{ \label{fig:rele_tv_40dB_s1} The relative errors of the time-varying filter estimation converge slower than with the subspace method. 
The relative errors of $\widehat{a}$ and $\widehat{b}$ are smaller than 5 \% only after 800 and 950 samples, respectively.
With the subspace method the relative errors are below 5 \% after 400 and 500 samples. }
\end{figure}

>>>>

\begin{quote}
%\vspace{-0.5cm}
\emph{The results of this chapter were published in Quintana Carapia, G., and Markovsky, I.,
"Input parameters estimation from time-varying measurements", Measurement Journal, Vol. 153, 2020,
ISSN 0263-2241, doi:10.1016/j.measurement.2019.107418. \nocite{QuintanaMEAS} } %\vfill{}
\end{quote}

\vfill{}

@@

\paragraph{Problem} 
Given the sequence of measured output observations $\widetilde{\mathbf{y}} = \left( \widetilde{y}(1),\ldots, \widetilde{y}(\color{blue}N\color{black})\right)$, with $\widetilde{y}(t) \in \mathbb{R}$, of a stable linear time-invariant system of order $n$, and static gain ${G}$, generated by an affine input $u(t) = {a} t + {b}$, estimate the parameters of the affine input, \textit{i.e.,} find the values of the parameters $\widehat{a}, \widehat{b} \in \mathbb{R}$ such that $\widehat{u}(t) = \widehat{a} t + \widehat{b}$ approximates $u$(t).
The measured observations $\widetilde{\mathbf{y}} = {\mathbf{y}} + \bm{\epsilon}$ are exact sensor responses ${\mathbf{y}}$ perturbed by additive noise  $\bm{\epsilon}$ assumed to be independent and normally distributed of zero mean and given variance $\sigma_{\epsilon}^2$.

@@

The subspace method processed online the sensor transient response.
The first estimation was obtained with $2n+1$ samples, where $n=2$ is the assumed order of the sensor.
The method updated recursively the value of the estimated parameters for each new collected sample, using the forgetting factor $\omega$ listed in Table \ref{table:lambdas}.
In Figure \ref{fig:rele_dd_40dB_s1} we observe the relative errors of the estimates $\widehat{a}$ and $\widehat{b}$ obtained when SNR = 40 dB. 
The relative errors are smaller than 5\% after 400 and 500 samples are processed, i.e., 0.04 s and 0.05 s, respectively.
As more samples are collected, the parameter estimation improves.
Figure \ref{fig:rele_SNR_dd_10000} shows the final value of the relative errors, found at $t=0.1$ s, for the different SNR values considered.
The relative errors are smaller than 2\% regardless of the measurement noise level.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_3.pdf} 
\caption{ \label{fig:rele_dd_40dB_s1} The relative errors of the affine input parameters estimates decrease as the subspace method processes more samples. The relative errors of the estimates $\widehat{a}$ and $\widehat{b}$ are smaller than 5\% after 400 and 500 samples, respectively ($T_s = 0.1$ ms). }
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_4.pdf} 
\caption{ \label{fig:rele_SNR_dd_10000} The minimum value of the estimation relative errors obtained with the subspace method is less than 2\% regardless of the SNR between 20 dB and 60 dB. }
\end{figure}

@@

\subsection{Results of the maximum-likelihood method}
\color{blue} 
The maximum-likelihood (ML) method estimates the affine input parameters from the sensor model transient response.
A total of 100 runs of the method were obtained, using different realizations of the measurement noise.
The measurement noise variance was set to have an SNR of 40 dB.
The ML method used the first 50 samples to initialize the optimization variables and updated the variables every $N_{\mathrm{s}} = 5$ samples.
Figure \ref{fig:rele_lo_40dB_s10} shows the average of the observed relative errors in the estimation of the parameters $\widehat{a}$, $\widehat{b}$, $\widehat{x}_{\mathrm{ini,1}}$, and $\widehat{x}_{\mathrm{ini,2}}$\color{black}.
The convergence of the ML estimates gives relative errors below 5\% after three iterations.
The largest relative error observed is in the scale velocity $\widehat{x}_{\mathrm{ini,2}}$ estimate, which is more sensitive than the other optimization variables.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_7.pdf} 
\caption{ \label{fig:rele_lo_40dB_s10} The affine input parameters and the sensor's initial conditions are estimated with the ML method. After three iterations, \color{blue} the average of the relative error is smaller than 5\% for each and every of the estimates. The estimate $\widehat{x}_{\mathrm{ini,2}}$ has the larger relative error near to 1\%. \color{black} }
\end{figure}

@@

Figure \ref{fig:rele_tv_40dB_s1} shows the relative errors of the estimates $\widehat{a}$ and $\widehat{b}$ computed with the TV filter after processing the sensor transient response.
The relative error of the slope estimate is below 5\% after 300 samples but the relative error of the intercept estimate is near 10\%.
The convergence rate of the estimate $\widehat{a}$ was similar to that of the subspace method.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\columnwidth]{./ChapterRampInput/fig/Fig_9.pdf} 
\caption{ \label{fig:rele_tv_40dB_s1} The relative errors of the time-varying filter estimation converge slower than with the subspace method. 
The relative errors of $\widehat{a}$ and $\widehat{b}$ are smaller than 5\% only after 800 and 950 samples, respectively.
With the subspace method the relative errors are below 5\% after 400 and 500 samples. }
\end{figure}

### 2020-09-09 ChapterStatisticalAnalysis/ChapterStatisticalAnalysis.tex
One before the very last

\begin{quote}
%\vspace{-0.5cm}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Bias and covariance of the least-squares estimate in a structured errors-in-variables problem", Computational Statistics \& Data Analysis journal, Vol. 144, 2020, ISSN 0167-9473, doi:10.1016/j.csda.2019.106893. \nocite{QuintanaCSDA} }\vfill{}
\end{quote}

%\vfill{}

@@

 where $\bm{\mathcal{H}}(\bm{\epsilon}) \in {\rm I\!R}^{\left(\color{blue}N\color{black}-n\right) \times \left(n+1\right)}$ is the block-Hankel matrix of $\color{blue}N\color{black}-n$ rows and $n$ columns

@@

Figure \ref{bias_sigma_NMC_unstr_str_n2} shows the empirical bias and the bias predictions, with their corresponding standard errors, \color{blue} for the unstructured EIV problem\color{black}.
The simulation settings for the structured and correlated EIV problem are described in the following subsection.
In the figure, it can be observed that the empirical bias $b_\mathrm{e}$ is proportional to the perturbation noise variance while the standard error $\sigma_\mathrm{e, err}$ is proportional to the perturbation noise standard deviation.
The bias predictions $b_\mathrm{p}$ and $b_{\widetilde{\mathrm{p}}}$ are accurate since they coincide with the empirical bias $b_\mathrm{e}$ in all the SNR interval for unstructured EIV problems. 
In both unstructured and structured EIV cases, the standard errors of the MC estimates $\sigma_{\mathrm{e, err}}$ and $\sigma_{\widetilde{\mathrm{p}}, \mathrm{err}}$ are smaller than the bias estimates $b_{\mathrm{e}}$ and $b_{\widetilde{\mathrm{p}}}$.
The bias estimates are spread near their sample means. 
The uncertainty is smaller than the bias, therefore, the MC simulation is meaningful.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_2.pdf} 
  \caption{ \label{bias_sigma_NMC_unstr_str_n2} 
  We observe the results of the LS solutions \color{blue} for the unstructured EIV problem\color{black}. These results are the empirical bias $b_{\mathrm{e}}$, the predicted bias from exact data $b_{\mathrm{p}}$, the predicted bias from observed data $b_{\widetilde{\mathrm{p}}}$, the empirical standard error $\sigma_{\mathrm{e, err}}$, and the standard error from the estimations using observed data $\sigma_{\widetilde{\mathrm{p}}, \mathrm{err}}$. The estimation biases are proportional to the perturbation variance and the estimation standard errors are proportional to the perturbation standard deviation. Since the standard errors are smaller than the biases, the MC simulation is meaningful. }
\end{figure}

@@

The plots \color{blue} in \color{black} Figure \ref{bias_sigma_NMC_str_str_n2} show the empirical bias, the bias predictions (\ref{eqn:biasE}) and (\ref{eqn:biasST}), and their corresponding standard errors, for the structured EIV problem.
The empirical bias $b_\mathrm{e}$ is proportional to the perturbation noise variance, and
the bias predictions $b_\mathrm{p}$ and $b_{\widetilde{\mathrm{p}}}$ coincide with the empirical bias $b_\mathrm{e}$ only for SNR above 40 dB.
This indicates that the SNR drops to a point where the constraint $\| \mathbf{M} \| < 1$ is no longer satisfied.
At an SNR of 30 dB the perturbation noise affects the bias prediction from observed data and it is three times smaller than the empirical bias.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_7.pdf} 
  \caption{ \label{bias_sigma_NMC_str_str_n2} 
  We observe the results of the LS solutions \color{blue} for the structured EIV problem\color{black}. These results are the empirical bias $b_{\mathrm{e}}$, the predicted bias from exact data $b_{\mathrm{p}}$, the predicted bias from observed data $b_{\widetilde{\mathrm{p}}}$, the standard error $\sigma_{\mathrm{e,err}}$ of the empirical bias, and the standard error $\sigma_{\widetilde{\mathrm{p}} \mathrm{,err}}$ of the the estimations bias computed using observed data. The estimation biases are proportional to the perturbation variance and the estimation standard errors are proportional to the perturbation standard deviation. Since the standard errors are smaller than the biases, the MC simulation is meaningful. }
\end{figure}

@@

The simulation results show that the LS solution of the structured and correlated EIV problem is more sensitive to the perturbation.
This represents a low limit in the SNR interval imposed by the noise level.
In practical applications it is common to have SNRs of 40 dB and the user needs to be aware of the prediction error that the method has.
We measure this prediction error with the mean squared error (MSE), defined as
\begin{equation} \mathrm{MSE} = \sigma^2 + b^2. \end{equation}
 By comparing the different MSEs to the CRLB of the structured EIV problem,
Figure \ref{fig:MSE_CRLB} shows that the MSEs has the same proportionality as the CRLB with respect to the disturbing noise variance.
The MSEs are three times larger than the CRLB.
Since the difference between $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ and the CRLB is lower than one order of magnitude, 
the LS estimation of the structured EIV problem produces results that are comparable to the ML estimation.
The $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ computed from observed data approaches the CRLB for SNR below 40 dB.
This is due to the constraint violation of the Taylor series expansion.

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_11.pdf}
  \caption{\label{fig:MSE_CRLB}
The mean squared errors of the LS estimate are close to the Cram\'er-Rao lower bound. This is a positive indication of the goodness of the LS estimator for the structured EIV problem. The mean squared error of the empirical estimates is represented by $\mathrm{MSE}_{\mathrm{e}}$, and those of the predictions are $\mathrm{MSE}_{\mathrm{p}}$ and $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$. The $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ is smaller than CRLB below 40 dB of SNR because of the introduced bias error, but the difference between $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ and the CRLB is lower than one order of magnitude.}
\end{figure}

\color{blue}
\subsection{Simulation results for the structured IV solution}

@@

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_12.pdf}
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_13.pdf}
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_14.pdf}
  \caption{\label{fig:bvMSE_IV} \color{blue} In a simulation, the solutions of the structured EIV and IV problems are empirically compared. The bias from solving the IV problem is noticeable smaller, by two orders of magnitude, than the one from solving the EIV problem. This argument is valid for SNRs higher that 35 dB. The obtained variances, on the other hand, are very similar in the same SNR interval. As a consequence, the mean-squared errors almost coincide.}
\end{figure}

>>>>

\begin{quote}
%\vspace{-0.5cm}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Bias and covariance of the least-squares estimate in a structured errors-in-variables problem", Computational Statistics \& Data Analysis journal, Vol. 144, 2020, ISSN 0167-9473, doi:10.1016/j.csda.2019.106893. \nocite{QuintanaCSDA} }%\vfill{}
\end{quote}

\vfill{}

@@

 where $\bm{\mathcal{H}}(\bm{\epsilon}) \in \mathbb{R}^{\left(\color{blue}N\color{black}-n\right) \times \left(n+1\right)}$ is the block-Hankel matrix of $\color{blue}N\color{black}-n$ rows and $n$ columns

@@

Figure \ref{fig:bias_sigma_NMC_unstr_str_n2} shows the empirical bias and the bias predictions, with their corresponding standard errors, \color{blue} for the unstructured EIV problem\color{black}.
The simulation settings for the structured and correlated EIV problem are described in the following subsection.
In the figure, it can be observed that the empirical bias $b_\mathrm{e}$ is proportional to the perturbation noise variance while the standard error $\sigma_\mathrm{e, err}$ is proportional to the perturbation noise standard deviation.
The bias predictions $b_\mathrm{p}$ and $b_{\widetilde{\mathrm{p}}}$ are accurate since they coincide with the empirical bias $b_\mathrm{e}$ in all the SNR interval for unstructured EIV problems. 
In both unstructured and structured EIV cases, the standard errors of the MC estimates $\sigma_{\mathrm{e, err}}$ and $\sigma_{\widetilde{\mathrm{p}}, \mathrm{err}}$ are smaller than the bias estimates $b_{\mathrm{e}}$ and $b_{\widetilde{\mathrm{p}}}$.
The bias estimates are spread near their sample means. 
The uncertainty is smaller than the bias, therefore, the MC simulation is meaningful.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_2.pdf} 
  \caption{ \label{fig:bias_sigma_NMC_unstr_str_n2} 
  We observe the results of the LS solutions \color{blue} for the unstructured EIV problem\color{black}. These results are the empirical bias $b_{\mathrm{e}}$, the predicted bias from exact data $b_{\mathrm{p}}$, the predicted bias from observed data $b_{\widetilde{\mathrm{p}}}$, the empirical standard error $\sigma_{\mathrm{e, err}}$, and the standard error from the estimations using observed data $\sigma_{\widetilde{\mathrm{p}}, \mathrm{err}}$. The estimation biases are proportional to the perturbation variance and the estimation standard errors are proportional to the perturbation standard deviation. Since the standard errors are smaller than the biases, the MC simulation is meaningful. }
\end{figure}

@@

The plots \color{blue} in \color{black} Figure \ref{fig:bias_sigma_NMC_str_str_n2} show the empirical bias, the bias predictions (\ref{eqn:biasE}) and (\ref{eqn:biasST}), and their corresponding standard errors, for the structured EIV problem.
The empirical bias $b_\mathrm{e}$ is proportional to the perturbation noise variance, and
the bias predictions $b_\mathrm{p}$ and $b_{\widetilde{\mathrm{p}}}$ coincide with the empirical bias $b_\mathrm{e}$ only for SNR above 40 dB.
This indicates that the SNR drops to a point where the constraint $\| \mathbf{M} \| < 1$ is no longer satisfied.
At an SNR of 30 dB the perturbation noise affects the bias prediction from observed data and it is three times smaller than the empirical bias.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_7.pdf} 
  \caption{ \label{fig:bias_sigma_NMC_str_str_n2} 
  We observe the results of the LS solutions \color{blue} for the structured EIV problem\color{black}. These results are the empirical bias $b_{\mathrm{e}}$, the predicted bias from exact data $b_{\mathrm{p}}$, the predicted bias from observed data $b_{\widetilde{\mathrm{p}}}$, the standard error $\sigma_{\mathrm{e,err}}$ of the empirical bias, and the standard error $\sigma_{\widetilde{\mathrm{p}} \mathrm{,err}}$ of the the estimations bias computed using observed data. The estimation biases are proportional to the perturbation variance and the estimation standard errors are proportional to the perturbation standard deviation. Since the standard errors are smaller than the biases, the MC simulation is meaningful. }
\end{figure}

@@

The simulation results show that the LS solution of the structured and correlated EIV problem is more sensitive to the perturbation.
This represents a low limit in the SNR interval imposed by the noise level.
In practical applications it is common to have SNRs of 40 dB and the user needs to be aware of the prediction error that the method has.
We measure this prediction error with the mean squared error (MSE), defined as
\begin{equation} \mathrm{MSE} = \sigma^2 + b^2. \end{equation}
 By comparing the different MSEs to the CRLB of the structured EIV problem,
Figure \ref{fig:MSE_CRLB_str_stat} shows that the MSEs has the same proportionality as the CRLB with respect to the disturbing noise variance.
The MSEs are three times larger than the CRLB.
Since the difference between $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ and the CRLB is lower than one order of magnitude, 
the LS estimation of the structured EIV problem produces results that are comparable to the ML estimation.
The $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ computed from observed data approaches the CRLB for SNR below 40 dB.
This is due to the constraint violation of the Taylor series expansion.

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_11.pdf}
  \caption{\label{fig:MSE_CRLB_str_stat}
The mean squared errors of the LS estimate are close to the Cram\'er-Rao lower bound. This is a positive indication of the goodness of the LS estimator for the structured EIV problem. The mean squared error of the empirical estimates is represented by $\mathrm{MSE}_{\mathrm{e}}$, and those of the predictions are $\mathrm{MSE}_{\mathrm{p}}$ and $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$. The $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ is smaller than CRLB below 40 dB of SNR because of the introduced bias error, but the difference between $\mathrm{MSE}_{\widetilde{\mathrm{p}}}$ and the CRLB is lower than one order of magnitude.}
\end{figure}

\color{blue}

\subsection{Simulation results observed when the perturbation noise does not concord with the type of perturbation assumed by the derived expressions}

In this section, the numerical study of the expressions that calculate the step input estimation bias and variance considers the situation when the perturbation noise is not in agreement with the assumptions made during the analysis and the derivation of the predicting expressions.  
In other words, the unstructured perturbation is used in the expressions derived for the structured case, and the structured perturbation is used in the expressions derived for the unstructured case. 
Two Monte Carlo simulations, each one with $N_{MC} = 10^6$ runs, were conducted and the relevant results are illustrated in Figures \ref{fig:unstrFormula_strData} and \ref{fig:strFormula_unstrData}. 
It is expected that the performance in these conditions is very far from that obtained when using the expressions in concordance with the perturbation type they were derived for.
The results confirm this argument, since the relative errors are in general close to 100\%.
An exception is the variance prediction computed with the formulas derived for the unstructured case, but using structured perturbation. 
Only in this combination, the relative error of the variance prediction is aroun 10\% for SNR below 70 dB.

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_12.pdf}
  \caption{\label{fig:unstrFormula_strData} \color{blue} We observe the results obtained from the Monte Carlo simulation, when the perturbation noise is structured and we use the predicting expressions that were derived assuming the perturbation noise is unstructured. A comparison of the empirical and the predicted bias and variance of the input estimation shows that the prediction formulas fail, since the relative errors between the empirical and the predicted statistical moments are larger than 10\%.}
\end{figure}

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_13.pdf}
  \caption{\label{fig:strFormula_unstrData} \color{blue} We observe the results obtained from the Monte Carlo simulation, when the perturbation noise is unstructured and we use the prediction expressions that were derived assuming the perturbation noise is structured. A comparison of the empirical and the predicted bias and variance of the input estimation shows that in these conditions, the derived expressions fail to predict the statistical moments. If the perturbation noise does not have the structure assumed by the prediction expressions, the relative error remains high above 10\% in all the SNR interval. }
\end{figure}

\subsection{Simulation results for the structured IV solution}

@@

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_14.pdf}
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_15.pdf}
  \includegraphics[width=0.69\columnwidth]{./ChapterStatisticalAnalysis/fig/Fig_16.pdf}
  \caption{\label{fig:bvMSE_IV} \color{blue} In a simulation, the solutions of the structured EIV and IV problems are empirically compared. The bias from solving the IV problem is noticeable smaller, by two orders of magnitude, than the one from solving the EIV problem. This argument is valid for SNRs higher that 35 dB. The obtained variances, on the other hand, are very similar in the same SNR interval. As a consequence, the mean-squared errors almost coincide.}
\end{figure}
